\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Vatsalya Singh}} & \faEnvelope \hspace{1pt} \href{mailto:vatsalyasingh218@gmail.com}{vatsalyasingh218@gmail.com}\\
   4\textsuperscript{th}  Year Undergraduate & \faPhone \hspace{1pt}\href{tel:7011589138}{+91-7011-589-138} \\
  Department Of Computer Science Engineering  & \faLinkedin \hspace{1pt} \href{https://www.linkedin.com/in/vatsalyasingh/}{Vatsalya Singh} \\
    Sikkim Manipal Institute of technology, Majitar, East Sikkim, India & \faGithub \hspace{1pt}\href{https://github.com/DialgicMew}{DialgicMew} \\

\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sikkim Manipal Institute of Technology}{Sikkim, India}
      {B.Tech in Computer Science and Engineering;  CGPA: 8.10}{Aug. 2017 -- On-Going}
    \resumeSubheading
      {Ahlcon International School}{Delhi, India}
      {Senior Secondary Education(CBSE), PCM;  Percent: 73.4\%}{May. 2015 -- March. 2017}
      \resumeSubheading
      {Delhi Public School}{Noida, India}
      {High School Education;  CGPA: 9.20}{April. 2003 -- March. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deutsche Telekom Digital Labs}{Gurugram, India}
      {Intern}{June. 2020 – Aug. 2020}
      \resumeItemListStart
        \resumeItem{Tensorflow}
         {My internship here at DTDL was an amazing learning experience. I completed 3 projects and 1 POC successfully. My projects have been deployed on the company servers and are being used by the employees daily. I worked on Kibana, wherein I learned about data visualization. I worked on Jenkins; a tool that is used for CI/CD pipeline creation, to save precious amounts of time for the Dev team.}
      \resumeItemListEnd
    \resumeSubheading
      {Tech Mahindra}{Intern June. 2019 – July. 2019}
      {Intern}{Intern June. 2019 – July. 2019}
      \resumeItemListStart
        \resumeItem{Tensorflow}
         {I worked as a web development intern at Tech Mahindra. I had a very dynamic role during the time there. I worked on CSS correction for most of the time, my duties were also of analysing SRS of multiple projects. I worked with a team of developers who were very skilled at their work. They guided me and helped me overcome the challenges I faced.}
      \resumeItemListEnd
    \resumeSubheading
      {Reliance Industries LTD.}{Mumbai, India}
      {Intern}{May. 2019 – June. 2019}
      \resumeItemListStart
        \resumeItem{Tensorflow}
         {I worked as a web development intern at Reliance Industries ltd., Navi Mumbai. I was assigned to a project on chatbots based to Natural Language processing. I used a tool by Google called DialogFlow for the same. The development was done using NodeJS, Angular and database was maintained in Firebase which was done by DialogFlow.}
      \resumeItemListEnd
    \resumeSubheading
      {Lava international}{Noida, India}
      {Intern}{May. 2018 - June. 2018}
      \resumeItemListStart
        \resumeItem{Tensorflow}
         {I worked as an intern at Lava International, Noida for about 30 days in which I learnt about database handling and connectivity using Java. I learnt bits and pieces of PHP which was required for connection to the database.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \projectItem{GuruChela App}
      {GuruChela is a cross-platform application for a client (Mrs. Swati Kumari) which aims to connect teachers and students. This application is on the Play Store and can be found at \href{http://bit.ly/GuruChela}{\textcolor{BurntOrange}{GuruChela}}.}
    \projectItem{Thank You Board Web-App}
      {A public thankyou board built on React, Node.js, MongoDB, and Socket.io. It is Web-App in which a team can create a board and use to it thank each other in Realtime by leaving real looking post-it notes.}
    \projectItem{London Street Mobile App}
      {Food delivery system as a project for a restaurant. Understanding the client's exact needs and delivering a personalised product for him was a tough task.}
    \projectItem{P2p Food Delivery System}
      {Created a cross-platform e-commerce application which will make homemade food available to everyone. The idea behind the project was to provide for homemakers with a platform.}
    \projectItem{Virtual Assistant Web-App}
      {This app is a virtual assistant and works as a chatbot as well; built using DialogFlow, Angular, NodeJS. This application can be trained for multiple day to day purposes.}
    \projectItem{E-Commerce Website}
      {My first freelance project which is for client (Mrs. Sapna Bhushan). It is a simple well-designed e-commerce website built on basic technologies like HTML, CSS, JavaScript.\href{https://www.tilkutkhaja.com/}{\textcolor{BurntOrange}{TilkutKhaja}}}

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C++, Dart, C, JavaScript, Java, Python, SQL}
     
   }
   \item{
     \textbf{Technologies}{: Flutter, React.js, Jenkins, Node.js, MongoDB, FireBase, Kibana }
   }
   
   
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
